\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
results:additional information subsection

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
	E1-OLD & 19/19 & 100\% & 1:01 \\ %medians of only finished: 1:01
	E2-NEW & 18/19 & 95\% & 3:32 \\ %medians of only finished: 3:22
	E2-OLD & 16/19 & 84\% & 5:00 \\ %medians of only finished: 3:13
	E3-NEW & 13/20 & 65\% & 20:56 \\ %medians of only finished: 12:38
	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

\begin{table}
\centering
% Generated by attempts.R, and manually reordered:
\begin{tabular}{r c c c c c c}
& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
no bridge, no proxy & 17 & 13 &  &  &  &  \\
obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
meek-google, no proxy &  &  &  &  & 5 & 4 \\
meek-azure, no proxy &  &  &  &  & 1 & 1 \\
no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
DNF &  &  & 1 & 3 & 7 & 10 \\
\end{tabular}
\caption{
Bridge--proxy combinations that led to the first successful bootstrap
in each environment and interface.
Most E1 participants used a direct connection,
but a few tried a built-in obfs3 bridge.
All the E2 participants who succeeded,
did so with obfs3 (the recommended bridge type)---none tried
a different bridge before obfs3.
All of the successful E3 participants, but one,
used one of the meek bridges.
The remaining E3 participant succeeded in an unexpected way:
by searching the web for an open proxy and configuring it
as the proxy setting.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

\subsubsection{Additional Information}

@@

People spent a lot of time just waiting at the progress bar.

Talk about the notion of ``active time,'' which is just time not spent on the progress screen.

%\begin{table}
%\centering
%	\begin{tabular}{c r r r r }
%	 & First & Proxy & Bridge & Summary \\
%	\noalign{\hrule}
%	All & 22\% & 57\% & 19\% & 2\% \\
%	NEW & 40\% & 31\% & 19\% & 9\% \\ 
%	OLD & 18\% & 63\% & 19\% & 0\% \\
%	E1 & 45\% & 22\% & 32\% & 1\% \\
%	E2 & 29\% & 48\% & 20\% & 2\% \\
%	E3 & 19\% & 61\% & 18\% & 2\% \\
%	\end{tabular}
%\caption{active time} 
%\label{table:active_time}
%\end{table}

% statistical tests
The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)

>>>>

\begin{table}[t]
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
	E1-OLD & 19/19 & 100\% & 1:01 \\ %medians of only finished: 1:01
	E2-NEW & 18/19 & 95\% & 3:32 \\ %medians of only finished: 3:22
	E2-OLD & 16/19 & 84\% & 5:00 \\ %medians of only finished: 3:13
	E3-NEW & 13/20 & 65\% & 20:56 \\ %medians of only finished: 12:38
	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

\begin{table}[t]
\centering
% Generated by attempts.R, and manually reordered:
\begin{tabular}{r c c c c c c}
& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
no bridge, no proxy & 17 & 13 &  &  &  &  \\
obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
meek-google, no proxy &  &  &  &  & 5 & 4 \\
meek-azure, no proxy &  &  &  &  & 1 & 1 \\
no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
DNF &  &  & 1 & 3 & 7 & 10 \\
\end{tabular}
\caption{
Bridge--proxy combinations that led to the first successful bootstrap
in each environment and interface.
Most E1 participants used a direct connection,
but a few tried a built-in obfs3 bridge.
All the E2 participants who succeeded,
did so with obfs3 (the recommended bridge type)---none tried
a different bridge before obfs3.
All of the successful E3 participants, but one,
used one of the meek bridges.
The remaining E3 participant succeeded in an unexpected way:
by searching the web for an open proxy and configuring it
as the proxy setting.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

\subsubsection{Additional information} 
While we did not find a statistically significant difference between the overall time to success between the old and new versions of the interface, the time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen.

We define the time participants not on the progress screen as the amount of time they actively spent configuring their connection. This is a simplified notion the time participants spent configuring, since some participants waited at the progress screen without doing anything while others searched for help on the web while they were waiting. However, participants with the new and old interface were equally likely to exhibit this behavior. Participants with the new interface showed a statistically significant reduction in the overall time configuring the interface (Mann-Whitney W = 997, p-value = 0.0001571). 
%The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)

We summarize each participant's actions throughout the experiment in Figure~\ref{fig:all-participant-edges}. Each row in Figure~\ref{fig:all-participant-edges} corresponds to a participant in our experiment. The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@
